
---
title: Disaster Affected Statistics report.|


output: 
 html_document:
   theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
   highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
   smart: true
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scroll: false
   numbers_sections: true
   fig_width: 7
   fig_height: 6
   fig_caption: true
   df_print: paged

runtime: shiny   
params:

  m: NA
  n: NA
  s: NA
  o: NA 
  z: NA
  minimum: 
    label: "Minimum:"
    value: 100
    input: slider
    min: 0
    max: 1000
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1234)
library(knitr)
library(mapview)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(purrr)

```
# Introduction

In this section, users will be able to view the statistics table that shows the total extent and impact of natural hazards on the population, land cover, points of interest, and infrastructure data layers. Additionally, users can also access the statistical table

## Disaster impact on assets map

The below map shows the impact of hazard on the land cover, point of interest, population, and Infrastructure areas map.

```{r echo=FALSE, message=TRUE, paged.print=FALSE,warning=FALSE}

params$m

```
*Figure 1: Shows the impact of disaster on assets map.* 

## Disaster Interest on Population map

The below map shows the impact of natural hazard on the population data sets users can see in each pixel how many numbers of people.

```{r echo=FALSE, message=TRUE, paged.print=FALSE,warning=FALSE}

mapview(params$o, col.regions = params$z)


```
*Figure 2: Shows the impact of hazard on Population map.* 


## Disaster Statistic Table:

The table below shows disaster-related statistical information that provides data on the impact of natural hazards on population, land cover, points of interest, and infrastructure information. 

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

datatable(data.frame(params$n),options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))

```


### Meta data
Below, we can find the metadata information, which provides detailed insights and descriptions about the data set you are referring to.
```{r echo=FALSE, message=TRUE, paged.print=FALSE}

datatable(data.frame(params$s),options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))


```


