
---
title: Land Cover Extent Statistics Report|

output: 
 html_document:
   theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
   highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
   smart: true
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scroll: false
   numbers_sections: true
   fig_width: 7
   fig_height: 6
   fig_caption: true
   df_print: paged

runtime: shiny   
params:

  n: NA
  m: NA
  o: NA
  p: NA
  q: NA
  s: NA
  
  minimum: 
    label: "Minimum:"
    value: 100
    input: slider
    min: 0
    max: 1000
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1234)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(purrr)

```
# Introduction 

This report will provide users with information on the total administrative boundaries, land cover, and the extent of hazard areas through maps. It will include a statistical table offering an overview of the different land cover classes, along with their respective percentages. Additionally, the report will feature graphs illustrating the distribution of land cover datasets by area and percentage. Lastly, it will also contain metadata information related to the data presented..


## Hazard extent and impact Map

The map below provides a clear depiction of various land cover types, along with administrative boundaries and hazard layer information. 

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults


                params$m



 
```

*Figure 1: Total hazard extent and Hazard area map.* 

## Imact of Hazard on land cover:

The table showcases the impact of hazards on land cover. Users can observe the approximate quantity of affected land areas and the corresponding percentage of land cover influenced by these hazards.

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults

datatable(data.frame(params$o),options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))

    

```

*Table 1: Hazard area on land cover and percentage table.*


The bar graph below illustrates the proportions of different land cover types affected within a specific region. This visual representation provides a comparative display of the areas various land cover types exposed to hazard.

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults

params$q


```
*Figure 2:  land cover area affected.* 

The bar graph below illustrates the proportions of different land cover types affected within a specific region. This visual representation provides a comparative display the percentage of various land  types are exposed to hazard. 


```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults

params$p


```
*Figure 3: Percentage of land cover affected.* 





### Meta data  

Below, we can find the metadata information, which provides detailed insights and descriptions about the data set you are referring to.

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

datatable(data.frame(params$s),options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))


```

