
---
title: Point of Interest Statistic report.|


output: 
 html_document:
   theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
   highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
   smart: true
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scroll: false
   numbers_sections: true
   fig_width: 7
   fig_height: 6
   fig_caption: true
   df_print: paged

runtime: shiny   
params:

  m: NA
  n: NA
  s: NA
  minimum: 
    label: "Minimum:"
    value: 100
    input: slider
    min: 0
    max: 1000
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1234)
library(knitr)
library(mapview)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(purrr)

```



# Introduction
In this report the users will be able to see the Point of interest layer the map displays below. The table shows the  Statistics information.

## Point of Interest-map

The Point of interest map below offers comprehensive insights into a variety of essential indicators, providing a detailed and informative perspective on the  point of interest landscape.

```{r echo=FALSE, message=TRUE, paged.print=FALSE,warning=FALSE}

params$m

```
*Figure 1: Shows the Point of interest map.* 

##  Point of Interest Statistic Table:

The table below shows the total Point of interest data it provides detail information of the different types of point of Interest Statistic.

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

datatable(data.frame(params$n),options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))

```


### Meta data
Below, we can find the metadata information, which provides detailed insights and descriptions about the data set you are referring to.
```{r echo=FALSE, message=TRUE, paged.print=FALSE}

datatable(data.frame(params$s),options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))


```


