
---
title: Land Cover Extent Statistics Report|

output: 
 html_document:
   theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
   highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
   smart: true
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scroll: false
   numbers_sections: true
   fig_width: 7
   fig_height: 6
   fig_caption: true
   df_print: paged

runtime: shiny   
params:

  n: NA
  m: NA
  o: NA
  p: NA
  q: NA
  s: NA
  
  minimum: 
    label: "Minimum:"
    value: 100
    input: slider
    min: 0
    max: 1000
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1234)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(purrr)

```
# Introduction 

This report will provide users with information on the total administrative boundaries, land cover, and the extent of hazard areas through the map. It will include a statistical table of the total land cover area around the region. This report will also provide some graphs showcasing the area and percentage of the land cover. Lastly, it will also contain metadata information related to the data presented.


## Land Cover extent Map

The map below provides a clear depiction of various land cover types, administrative boundaries, and hazard layer information. Click on the button on the right side of the map to change the layers and visualize the data sets. 

```{r echo=FALSE, message=TRUE, paged.print=FALSE}
# All defaults
          params$m
```

*Figure 1: Total hazard extent and Hazard area map.* 

## Land Cover Statistics Information :

The table offers detailed information regarding the various land cover types. Users can access information about the land cover area as well as the corresponding percentage within the administrative region.

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults

datatable(data.frame(params$o),options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))

```

*Table 1: Land cover and Percentage table.*


The bar graph below illustrates the proportions of different land cover types within a specific region. This visual representation provides a comparative display of the areas of various land cover types.

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults

params$q


```
*Figure 2:  land cover area* 

The bar graph below illustrates the proportions of different land cover types within a specific region. This visual representation provides a comparative display the percentage of various land  types.


```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults

params$p


```
*Figure 3: Percentage of land cover* 




### Meta data  

Below, we can find the metadata information, which provides detailed insights and descriptions about the data set you are referring to.

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

datatable(data.frame(params$s),options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))


```

